---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# rjd3providers

<!-- badges: start -->
<!-- badges: end -->

## Overview

rjd3providers provides tools to explore the default time series providers (.xslx, .csv, .txt and .xml files) for JDemetra+ v3.x Graphical User Interface. It allows to manipulate raw series files. For example, using this R package, you will be able to:

- change the **path** of the raw data
- change the file **type**
- manipulate **monikers**
- change file **read properties**


## Installation

rjd3providers relies on the [rJava](https://cran.r-project.org/web/packages/rJava/index.html) package.

Running rjd3 packages requires **Java 17 or higher**. How to set up such a configuration in R is explained [here](https://jdemetra-new-documentation.netlify.app/#Rconfig) 

To get the current stable version (from the latest release):

``` {r installation-release, echo = TRUE, eval = FALSE}
# install.packages("remotes")
remotes::install_github("rjdverse/rjd3toolkit@*release")
remotes::install_github("rjdverse/rjd3providers@*release")
```

To get the current development version from GitHub:

``` {r installation-devel, echo = TRUE, eval = FALSE}
# install.packages("remotes")
remotes::install_github("rjdverse/rjd3providers")
```


## Usage

### Generate all the TS information 

``` {r generate_info, echo = TRUE, eval = TRUE}
library("rjd3providers")

xlsx_file <- paste0(system.file("examples", package = "rjd3providers"), "/Insee.xlsx")
spreadsheet_content(xlsx_file)

ts1 <- spreadsheet_series(file = xlsx_file, sheet = 1L, series = 3)
str(ts1)

all_ts <- spreadsheet_data(file = xlsx_file, sheet = 2L)
```

### Change path of an SA-ITEM

``` {r change_path, echo = TRUE, eval = FALSE}
# install.packages("remotes")
# remotes::install_github("rjdverse/rjd3workspace")

new_jd3_ts <- spreadsheet_series(file = xlsx_file, sheet = 1L, series = 3)
rjd3workspace::set_ts(jsap1, 2, new_jd3_ts)

# open an existing WS
ws <- rjd3workspace::.jws_open(file = some_ws_path)
# open an existing SAP
jsap <- rjd3workspace::.jws_sap(ws, idx = 1L)

# Change the TS object with the new moniker
rjd3workspace::set_ts(jsap = jsap, idx = 1, y = ts1)

rjd3workspace::save_workspace(jws = ws_path, file = "./ws/ws_path_v3.xml", replace = TRUE)
```


## Contributing

Any contribution is welcome and should be done through pull requests and/or issues.

## Licensing

The code of this project is licensed under the [European Union Public Licence (EUPL)](https://joinup.ec.europa.eu/page/eupl-text-11-12).
