---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# rjd3providers

<!-- badges: start -->
<!-- badges: end -->

## Overview

rjd3providers provides tools to explore the default time series providers (.xslx, .csv, .txt and .xml files). With this package you can now manipulate raw series files. For example, using this R package, you will be able to:

- change the **path** of the raw data
- change the file **type**
- manipulate **monikers**
- change file **read properties**


## Installation

Running rjd3 packages requires Java 17 or higher. How to set up such a configuration in R is explained [here](https://jdemetra-new-documentation.netlify.app/#installing-the-software) 

To get the current stable version (from the latest release):

``` {r installation-release, echo = TRUE, eval = FALSE}
# install.packages("remotes")
remotes::install_github("rjdemetra/rjd3toolkit@*release")
remotes::install_github("rjdemetra/rjd3providers@*release")
```

To get the current development version from GitHub:

``` {r installation-devel, echo = TRUE, eval = FALSE}
# install.packages("remotes")
remotes::install_github("rjdemetra/rjd3providers")
```


## Usage

rjd3providers relies on the [rJava](https://cran.r-project.org/web/packages/rJava/index.html) package and Java SE 17 or later version is required.

### Generate all the TS information 

``` {r generate_info, echo = TRUE, eval = TRUE}
library("rjd3providers")

xlsx_file <- paste0(system.file("examples", package = "rjd3providers"), "/Insee.xlsx")
spreadsheet_content(xlsx_file)

ts1 <- spreadsheet_series(file = xlsx_file, sheet = 1L, series = 3)
str(ts1)

all_ts <- spreadsheet_data(file = xlsx_file, sheet = 2L)
```

### Change path of an SA-ITEM

``` {r change_path, echo = TRUE, eval = FALSE}
# install.packages("remotes")
# remotes::install_github("rjdemetra/rjdemetra3")

new_jd3_ts <- spreadsheet_series(file = xlsx_file, sheet = 1L, series = 3)
rjdemetra3::set_ts(jsap1, 2, new_jd3_ts)

# open an existing WS
ws <- rjdemetra3::.jws_open(file = some_ws_path)
# open an existing SAP
jsap <- rjdemetra3::.jws_sap(ws, idx = 1L)

# Change the TS object with the new moniker
rjdemetra3::set_ts(jsap = jsap, idx = 1, y = ts1)

rjdemetra3::save_workspace(jws = ws_path, file = "./ws/ws_path_v3.xml", replace = TRUE)
```


## Contributing

Any contribution is welcome and should be done through pull requests and/or issues.

## Licensing

The code of this project is licensed under the [European Union Public Licence (EUPL)](https://joinup.ec.europa.eu/page/eupl-text-11-12).
